\bf Faster Neural Machine Translation Inference

### 2018-02-02 fast-beam/fast-beam.tex
fast beam paper

REDO

Deep learning models have been successfully used on many machine learning task in recent years in areas as diverse as computer vision and natural language processing. This success have been followed by the rush to put these model into production. However, the computational resources required in order to run these models have ben chanllenging. One possible solution involves creating faster models that can approximate the original model~\citep{DBLP:conf/emnlp/KimR16}. Another solution is tackling specific computationally intensive functions by approximating them (??? softmax).

Most current neural MT models follow an encoder-decoder architecture. The encoder calculates the word and sentence embeddings while the decoder generates the output sentence. The architecture within the encoder is still a subject of much research. ~\cite{kalchbrenner13emnlp} used a convolution to encode the input and a recurrent neural network (RNN) for the decoder. RNNs was used for both encoding and decoding in (??? who used RNN 1st). ~\cite{Sutskever:2014:SSL:2969033.2969173} significantly improved translation quality by using LSTM was used in each RNN node. ~\cite{D14-1179} used GRU that has the required properties of LSTM but is computationally cheaper. ~\cite{DBLP:journals/corr/BahdanauCB14} added attention model which improved translation at a cost of slower speed.

There has been recent attempts to move away from the sequence-to-sequence models of RNN encoder-decoder. Some justify their architecture on faster inference as well as better translation results. ~\cite{DBLP:journals/corr/VaswaniSPUJGKP17} and (??? course-to-fine) has been proposed as a fast alternatives to RNN-based models as it is possible to process more of the units in parallel.

It has been noticed that half precision arithmetic can be used for deep learning model without significan loss of model quality~\citep{DBLP:journals/corr/abs-1710-03740}. Other solutions include specialized hardware, the most popular being graphical processing units (GPU) but other hardware such as custom processors TPU~\citep{DBLP:journals/corr/JouppiYPPABBBBB17}, FPGA~\citep{DBLP:journals/corr/LaceyTA16} have been used.

Many of these optimization are general purpose improvements for deep learning models, regardless of the task it is being used in. ~\cite{DBLP:conf/emnlp/Devlin17} is a noticeable machhine translation-specific optimization which describe the speed improvements that can be obtained by techniques such as the use of half-precision, model changes and pre-computation.

@@

For future work, we would like to apply our optimization for other NLP and deep-learning tasks. We are also interested in further optimization of the output layer in NMT, specifically the matrix multiplication which currrently take up ??? of the translation time.

>>>>

Deep-learning models has been successfully used on many machine learning task in recent years in areas as diverse as computer vision and natural language processing. This success have been followed by the rush to put these model into production. The computational resources required in order to run these models has been challenging but, fortunately, there has been a lot work to meet this challenge.

Hardware accelerators such as GPUs are very popular but other specialized hardware such as custom processors~\citep{DBLP:journals/corr/JouppiYPPABBBBB17} and FPGA~\citep{DBLP:journals/corr/LaceyTA16} have been used. Hardware-supported reduced precision is also an ideal way to speed up model inference~\citep{DBLP:journals/corr/abs-1710-03740}.

Simpler, faster models have been created that are as good, or almost as good, as more slower, more complex models~\citep{DBLP:journals/corr/BahdanauCB14}. Research have also gone into smaller, faster models that can approximate the original, slower, bigger model~\citep{DBLP:conf/emnlp/KimR16}. Some models have been justified as more suited for the parallel architecture of GPUs~\cite{DBLP:journals/corr/VaswaniSPUJGKP17}.

The speed of the softmax layer when used with large vocabularies have been looked at in~\citep{DBLP:journals/corr/GraveJCGJ16} but there have been many other attempts at faster softmax, for example~\cite{DBLP:journals/corr/abs-1301-3781}, ~\cite{Zoph-2016}.

There has been little work on batching algorithms, which is suprising considering its critical importance for fast model inference. ~\cite{Neubig-autobatching} describe an novel batching algorithm, however, its aim is to alleviate the burden on developers in batching of new models, not faster batching.

Our paper follows most closely on from ~\cite{DBLP:conf/emnlp/Devlin17} which achieved faster NMT inference mainly by novel implementation of an existing model. However, we differ by focusing on GPU implementation, and the output layer and batching algorithm which were not touched on by the previous work.

@@

For future work, we would like to apply our optimization for other NLP and deep-learning tasks. We are also interested in further optimization of the output layer in NMT, specifically the matrix multiplication which still takes up a significant proportion of the translation time.
